### 2019-10-21 Manuscript/Supplementary_Information/Supplementary_Information.tex
Updates from Overleaf

\noindent
$k_{e}$ is a proportionality constant ((m/yr)$^{1-m}$) and $m$ and $n$ are adjustable exponents that are kept as 0.5 and 1 as in \citet{Maffre2018a}. This formulation is close to the large-scale BQART model of \citet{Syvitski2007a}, but with the replacement of elevation with slope and without a temperature dependence, resulting in a functional form that more closely resembles the stream power law \citep{Davy2000a}. This formulation and these exponent values are supported by various compilations (e.g. \citealp{Lague2013a}) although \citet{Lague2013a} also suggests that there is variability in the proportionality constant that is difficult to capture at a global scale.

@@

We restricted the calculation of the weathering fluxes to the flux of dissolved Ca+Mg originating from continental silicate weathering, as they are the sole contributors to the long-term consumption of atmospheric \COtwo. To calculate this flux, we need to assign the concentration of Ca and Mg ($\chi_{CaMg}$) within the unweathered bedrock (Fig. \ref{fig:regolith_schematic}). Previous implementations of GEOCLIM have used bulk continental crust values across all exposed land, using the concept of ``diffuse lithology'' (it was assumed that the weathering rates of all rocks was the same for each continental grid element, provided that the grid element was submitted to the same climatic conditions). Given that the hypothesis we seek to test involves the varying concentration of cations in different lithologies, the diffuse lithology cannot be used anymore, and instead we have implemented a more realistic lithologically-resolved version of the model.

@@

The Ca+Mg concentrations of felsic (1,521~mol/m$^{3}$), intermediate (4,759~mol/m$^{3}$), and mafic (10,317~mol/m$^{3}$) lithologies are assigned based on the mean of data compiled from EarthChem (\url{www.earthchem.org/portal}). For metamorphic and siliciclastic lithologies, we explore a range of feasible Ca+Mg concentrations during calibration of the silicate weathering component of GEOCLIM (\textit{GEOCLIM Calibration}).

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{Manuscript/Figures/W_vs_r2.jpg}
    \caption{\textbf{A)} Modeled global \COtwo consumption vs. the coefficient of determination ($r^{2}$) between modeled and data-constrained \COtwo consumption in each of the watersheds. Each point represents model output using one of the 78,000 parameter combinations. \textbf{B)} Same as A, but zoomed to the plotting space with positive $r^{2}$'s. The black line represents the full range of estimates of the present-day global CO$_{2}$ emission rate compiled in \citet{Gerlach2011a}. The black box represents the preferred range of those estimates.}
    \label{fig:W_vs_r2}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{Manuscript/Figures/weathering_regolith_maps.jpg}
    \caption{Chemical weathering and regolith thickness maps for the parameter combination that produced that highest $r^{2}$ (Fig. \ref{fig:r2_cross_plot}B). Parameter values used for this combination are: $k_{d}=5\times10^{-4}$, $k_{w}=1$, $\sigma=-0.4$, $k_{rp}=1\times10^{-2}$, metamorphic$_{Ca+Mg}=2500$~mol/m$^{3}$, sediment$_{Ca+Mg}=2000$~mol/m$^{3}$.}
    \label{fig:weathering_regolith_maps}
\end{figure}

Experimental determinations of the activation energy ($E_a$; Equations \ref{eq:8} and \ref{eq:9}) associated with the weathering of silicate minerals are variable \citep{Brantley2003a}. However, multiple efforts to invert for $E_a$ in basaltic watersheds with varying temperature have yielded values (41.6 $\pm$ 3.2~kJ/mol in \citealp{Li2016a}; 42.3~kJ/mol in \citealp{Dessert2001a}) that are consistent with the lower end of activation energies of Ca+Mg bearing minerals in laboratory experiments such as that for diopside (40.5 $\pm$ 1.7~kJ/mol; \citealp{Knauss1993a}) and for labradorite (42.1~kJ/mol; \citealp{Carroll2005a}). We use the value of 42~kJ/mol in our model runs.

Within the equations that govern the silicate weathering component of GEOCLIM, we identify the less constrained parameters: the proportionality constant that modifies the dependence of dissolution rate on runoff and temperature ($k_{d}$; Equation \ref{eq:9}), the proportionality constant that modifies the dependence of dissolution rate on runoff only ($k_{w}$; Equation \ref{eq:9}), the power constant that modifies the dependence of dissolution rate on the time that a rock particle has spent in the regolith ($\sigma$; Equation \ref{eq:4}), and the proportionality constant that modifies the dependence of regolith production on runoff and temperature ($k_{rp}$; Equation \ref{eq:8}). Furthermore, the Ca+Mg concentrations of metamorphic and siliciclastic sediment grid cells are also difficult to define. We therefore allow these parameters to vary within reasonable bounds during the calibration stage of GEOCLIM and test 78,000 unique parameter combinations (Table \ref{tab:parameter_combinations}).

@@

We then compute spatially-resolved long-term \COtwo consumption (i.e. Ca+Mg fluxes) using present-day runoff (UNH/GRDC Composite Runoff Fields V1.0; \citealp{Fekete1999a}), temperature (CRU TS v.4.03; \citealp{Harris2013a}), and slope (Shuttle Radat Topography Mission; \citealp{Farr2007a}) fields. As described in the main text, we then sum the computed \COtwo consumption over large-scale watersheds that appear in the global compilation of \citet{Gaillardet1999a}, as well as smaller-scale watersheds of the Amazon Basin (HYBAM network) in the compilation of \citet{Moquet2011a, Moquet2016a, Moquet2018a}. 80 watersheds in total are used in this study. We calculate the coefficient of determination ($r^{2}$) between computed and measured \COtwo consumption in each of these basins:

@@

Global CO$_{2}$ consumption calculated from these 3,339 parameter combinations ranges from 2.7$\times10^{12}$~mol/yr to 7.1$\times10^{12}$~mol/yr, with a mean of 5.4$\times10^{12}$~mol/yr. These estimates fall within the range of those independently estimated in the literature for the present-day: the full range of estimates of the present-day global CO$_{2}$ emission rate compiled in \citet{Gerlach2011a} is 3.0--10.0$\times10^{12}$~mol/yr, with the preferred range of those estimates being 3.4--5.9$\times10^{12}$~mol/yr (Fig. \ref{fig:W_vs_r2}B).

@@

We use temperature and runoff fields from a subset of the GFDL CM2.0 experiments (\citealp{Delworth2006a, Delworth2006b}; available for download at \url{https://nomads.gfdl.noaa.gov/dods-data/gfdl_cm2_0/}) for the climate model component of GEOCLIM. These experiments were performed in order to explore the effect of various changes in forcing agents on climate since ca. 1860 at 2.0\degrees $\times$ 2.5\degrees resolution. In the ``1860 control'' experiment, forcing agents representative of conditions ca. 1860 (including \COtwo, CH$_{4}$, N$_{2}$O, O$_{3}$, sulfates, carbon, dust, sea salt, solar irradiance, and the distribution of land cover types) are held constant for 500 years after reaching equilibrium. \pCOtwo in 1860 is assumed to be 286~ppm. In the ``+1\%/yr to 2$\times$'' experiment, initial conditions are taken from the ``1860 control'' experiment, then \pCOtwo is prescribed to increase from 286~ppm at a compounded rate of +1\% per year for 70 years, when \pCOtwo reaches double (572~ppm) of the initial value. \pCOtwo is then held constant until the end of the 280 year experiment. All non-\COtwo forcing agents are held constant. The ``+1\%/yr to 4$\times$'' experiment is identical to the ``+1\%/yr to 2$\times$'' experiment, except that \pCOtwo is prescribed to increase for 140 years, when \pCOtwo reaches quadruple (1144~ppm) of the initial value. \pCOtwo is then held constant for 160 years. We take the mean of the last 100 years of each of these three experiments (when \pCOtwo is being held constant at its final level) to obtain temperature and runoff fields for 286, 572, and 1144~ppm respectively. Temperature and runoff fields for any arbitrary \pCOtwo value between 286 and 1144~ppm are obtained by linearly interpolating between the three modeled \pCOtwo levels.

@@

We use geological data to quantify the changes in the area of I\&NG over the past 20~m.y. (described in detail in \textit{Paleoshoreline Reconstruction and Geological Synthesis}). To generate the lithologic map used in the ``removed I\&NG'' scenario (Fig. \ref{fig:ING_fracs}), we remove all land associated with arc-continent collision in I\&NG. To generate the lithologic map used in the ``reduced I\&NG + Sunda Shelf'' scenarios (Fig. \ref{fig:ING_fracs}), we take the estimated paleoshorelines of I\&NG for 15, 10, and 5~Ma, then remove all land that falls outside of these bounds. The slope and lithologic classification of each pixel is identical to that of the present day, provided that these pixels fall within the estimated paleoshorelines of I\&NG for their respective time slice. We then add land that is not exposed today (i.e. the Sunda Shelf). However, the assignment of lithology, runoff, and slope for pixels on the Sunda Shelf is not trivial, given that the shelf is not currently exposed. As discussed in \textit{Paleoshoreline Reconstruction and Geological Synthesis}, the Sunda Shelf is a flat-lying, relatively stable platform of continental crust. Islands between Malaysia/Sumatra and Borneo are composed of granite and are surrounded by shallow marine siliciclastic sediments \citep{Darmadi2007a, Hall2009a, Hall2013b}. However, basement highs do not appear in the Gulf of Thailand, and seismic and drill core data suggest siliciclastic fluvial systems draining out toward the South China Sea when the shelf was exposed \citep{Darmadi2007a}. We therefore assign pixels of the Sunda Shelf between Malaysia/Sumatra and Borneo to be 50\% felsic and 50\% sediment, and pixels further to the north to be 100\% sediment. For the slope, we take the mean slope value (0.0038~m/m) of relatively flat land on eastern Sumatra, and assign this value to all pixels of the Sunda Shelf.  For the runoff, we linearly interpolate along latitude bands between present-day land pixels to obtain runoff values for the presently-submerged Sunda Shelf. This approach preserves large N-S variation in runoff associated with the large-scale Hadley circulation and therefore should be reasonable to first-order, although it does not accurately capture the smaller-scale interactions between land and ocean/atmosphere circulation.

To explore the sensitivity of our results to the inclusion of the Sunda Shelf, we also tested ``reduced I\&NG'' scenarios for 15, 10, and 5~Ma, which are identical to that of the ``reduced I\&NG + Sunda Shelf'' scenarios without the addition of the Sunda Shelf. We find that the estimated steady state \pCOtwo's for the ``reduced I\&NG'' scenarios are only marginally higher than those of the ``reduced I\&NG + Sunda Shelf'' scenarios (Fig. \ref{fig:scenario_pCO2_all}), suggesting that our results are insensitive to the inclusion of the Sunda Shelf. This insensitivity can be attributed to the low Ca+Mg concentrations of felsic and sediment lithologies in conjunction with the low relief across the shelf.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{Manuscript/Figures/pCO2_proxies.pdf}
    \caption{Proxy-based \pCOtwo estimates for the past 20~m.y. For the \citet{Foster2017a} data, error bars indicate standardized uncertainties. For the \citet{Ji2018a} data, error bars represent the 16-84$^{th}$ percentile of resampled estimates. The \citet{Bereiter2015a} data comes from the EPICA Dome C ice core.}
    \label{fig:pCO2_proxies}
\end{figure}

@@

\section*{Limitations and Future Directions}

As with any modeling study, there are limitations with the approach. We consider one of the current limitations to be the climate model component of GEOCLIM that was used in this study (GFDL CM2.0), which has a lower spatial resolution (2.0\degrees $\times$ 2.5\degrees) than what can be achieved with the latest climate models and computational resources. While this model is effective in capturing the large-scale climatology, using an updated climate model at higher resolution may result in runoff and temperature fields with different spatial distribution and sensitivities to elevation.

Another limitation associated with using a modern-day climate model, is that in the scenarios with varying shorelines, we hold the slope and lithology to be the same as the present-day in each pixel. This means that while we are changing the amount of emergent land, we are not changing the latitudinal or longitudinal position and are keeping the slope of any emerged pixel the same. Given that similar distributions of lithology and slope are reasonable in the past and that latitudinal translation has been relatively minor (Fig. XXX), we consider this simplification to be reasonable to first-order. However, implementing high-resolution climate models with both varying shorelines and changes in paleogeographic position for these scenarios is a valuable future direction. Additionally, such modeling efforts could give insight into whether associated changes in ocean and atmosphere circulation would have significantly modulated precipitation in I\&NG.  Given that precipitation in this region is primarily driven by large-scale convective upwelling leading to high precipitation over both land and water, the current approach is a reasonable approximation for I\&NG. However, for paleogeographic change that would have very significantly modified precipitation over broad swathes of land such as growth of the Himalaya, this approach of using modern climate model results is not viable.

Finally, although the silicate weathering component of GEOCLIM now implements lithology-dependent Ca+Mg concentration, our implementation does not include lithology-dependent kinetics of mineral dissolution. Relative to felsic lithologies, mafic lithologies contain a higher concentration of minerals with faster dissolution kinetics (e.g. plagioclase). However, Ca+Mg from both felsic and mafic lithologies is predominantly sourced from minerals with faster dissolution kinetics, and we therefore use the same chemical weathering formulation (including the same activation energy) across lithologies. We also do not include the effects of reverse weathering \citep{Michalopoulos1995a} as it is not clear how it should be parameterized and it is interpreted to be a relatively minor flux in the Cenozoic \citep{Isson2018a}. Formation of authigenic clays that scales with Ca and Mg concentration of riverine waters could decrease the \COtwo consumption associated with silicate weathering although the overall trend seen in this study would remain.

>>>>

\noindent
$k_{e}$ is a proportionality constant ((m/yr)$^{1-m}$) and $m$ and $n$ are adjustable exponents that are kept as 0.5 and 1 as in \citet{Maffre2018a}. This formulation is directly inspired from the stream power law \citep{Davy2000a}. This law and these exponent values are supported by various compilations (e.g. \citealp{Lague2013a}) although \citet{Lague2013a} also suggests that there is variability in the proportionality constant that is difficult to capture at a global scale.

@@

We restricted the calculation of the weathering fluxes to the flux of dissolved Ca+Mg originating from continental silicate weathering, as they are essential for the long-term consumption of atmospheric \COtwo through silicate weathering. To calculate this flux, we need to assign the concentration of Ca and Mg ($\chi_{CaMg}$) within the unweathered bedrock (Fig. \ref{fig:regolith_schematic}). Previous implementations of GEOCLIM have used a ``diffuse lithology'' where all exposed land is assigned the composition of bulk upper continental crust. Given that the hypothesis we seek to test involves the varying concentration of cations in different lithologies, the diffuse lithology approach cannot be used, and instead we have implemented a more realistic lithologically-resolved version of the model.

@@

The Ca+Mg concentrations of felsic (1,521~mol/m$^{3}$), intermediate (4,759~mol/m$^{3}$), and mafic (10,317~mol/m$^{3}$) lithologies are assigned based on the mean of data compiled from EarthChem (\url{www.earthchem.org/portal}; calculations made in the code with the repository). For metamorphic and siliciclastic lithologies, we explore a range of feasible Ca+Mg concentrations during calibration of the silicate weathering component of GEOCLIM (\textit{GEOCLIM Calibration}).

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{Manuscript/Figures/W_vs_r2.jpg}
    \caption{\textbf{A)} Modeled global \COtwo consumption vs. the coefficient of determination ($r^{2}$) between modeled and data-constrained \COtwo consumption in each of the watersheds. Each point represents model output using one of the 78,000 parameter combinations. \textbf{B)} Same as A, but zoomed to the plotting space with positive coefficient of determination values. The black line represents the full range of estimates of the present-day non-anthropogenic global CO$_{2}$ emission rate compiled in \citet{Gerlach2011a}. The black box represents the preferred range of these estimates preferred by \citet{Gerlach2011a}.}
    \label{fig:W_vs_r2}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{Manuscript/Figures/weathering_regolith_maps.jpg}
    \caption{Chemical weathering and regolith thickness maps associated with the GEOCLIM model run using the parameter combination that produced that highest $r^{2}$ (Fig. \ref{fig:r2_cross_plot}B). Parameter values used for this model run are: $k_{d}=5\times10^{-4}$, $k_{w}=1$, $\sigma=-0.4$, $k_{rp}=1\times10^{-2}$, metamorphic$_{Ca+Mg}=2500$~mol/m$^{3}$, sediment$_{Ca+Mg}=2000$~mol/m$^{3}$.}
    \label{fig:weathering_regolith_maps}
\end{figure}

Experimental determinations of the activation energy ($E_a$; Equations \ref{eq:8} and \ref{eq:9}) associated with the weathering of silicate minerals are variable \citep{Brantley2003a}. However, multiple efforts to invert for $E_a$ in basaltic watersheds with varying temperature have yielded values (41.6 $\pm$ 3.2~kJ/mol in \citealp{Li2016a}; 42.3~kJ/mol in \citealp{Dessert2001a}) that are consistent with the lower end of activation energies of Ca+Mg bearing minerals in laboratory experiments such as that for diopside (40.5 $\pm$ 1.7~kJ/mol; \citealp{Knauss1993a}) and for labradorite (42.1~kJ/mol; \citealp{Carroll2005a}). We use the value of 42~kJ/mol in our model runs. While we implement lithology-dependent Ca+Mg concentration, our implementation does not include lithology-dependent kinetics of mineral dissolution. Relative to felsic lithologies, mafic lithologies contain a higher concentration of minerals with faster dissolution kinetics (e.g. plagioclase). However, Ca+Mg from both felsic and mafic lithologies is predominantly sourced from minerals with faster dissolution kinetics, and we therefore use the same chemical weathering formulation (including the same activation energy) across lithologies.

Within the equations that govern the silicate weathering component of GEOCLIM, we identify the less constrained parameters: the proportionality constant that modifies the dependence of dissolution rate on runoff and temperature ($k_{d}$; Equation \ref{eq:9}), the proportionality constant that modifies the dependence of dissolution rate on runoff only ($k_{w}$; Equation \ref{eq:9}), the power constant that modifies the dependence of dissolution rate on the time that a rock particle has spent in the regolith ($\sigma$; Equation \ref{eq:4}), and the proportionality constant that modifies the dependence of regolith production on runoff and temperature ($k_{rp}$; Equation \ref{eq:8}). Furthermore, the Ca+Mg concentrations of metamorphic and siliciclastic sediment grid cells are also difficult to define. We therefore allow these parameters to vary within reasonable bounds during the calibration stage of GEOCLIM. In total, we test 78,000 unique parameter combinations (Fig. \ref{fig:r2_cross_plot}; Table \ref{tab:parameter_combinations}).

@@

We then compute spatially-resolved long-term \COtwo consumption (i.e. Ca+Mg fluxes) using present-day runoff (UNH/GRDC Composite Runoff Fields V1.0; \citealp{Fekete1999a}), temperature (CRU TS v.4.03; \citealp{Harris2013a}), and slope (Shuttle Radar Topography Mission; \citealp{Farr2007a}) fields. As described in the main text, we then sum the computed \COtwo consumption over large-scale watersheds that appear in the global compilation of \citet{Gaillardet1999a}, as well as smaller-scale watersheds of the Amazon Basin (HYBAM network) in the compilation of \citet{Moquet2011a, Moquet2016a, Moquet2018a}. Those lasts are nested watersheds, which means we have to subtract upstream weathering fluxes from downstream fluxes. Watersheds for which this subtraction yields an aberrant value are not considered. 80 watersheds in total are used in this study. We calculate the coefficient of determination ($r^{2}$) between computed and measured \COtwo consumption in each of these basins:

@@

Global CO$_{2}$ consumption calculated from these 3,339 parameter combinations ranges from 2.7$\times10^{12}$~mol/yr to 7.1$\times10^{12}$~mol/yr, with a mean of 5.4$\times10^{12}$~mol/yr. These estimates fall within the range of those independently estimated in the literature for the present-day: the full range of estimates of the present-day non-anthropogenic global CO$_{2}$ emission rate compiled in \citet{Gerlach2011a} is 3.0--10.0$\times10^{12}$~mol/yr, with the preferred range of those estimates being 3.4--5.9$\times10^{12}$~mol/yr (Fig. \ref{fig:W_vs_r2}B).
Each parameter combination predicts a different total \COtwo consumption that should match the \COtwo degassing at steady-state. Hence, in the GEOCLIM experiments, each parameter combination is used with its corresponding steady-state \COtwo degassing. In these estimates we are not including the effects of reverse weathering \citep{Michalopoulos1995a} as it is not clear how it should be parameterized and it is interpreted to be a relatively minor flux in the Cenozoic \citep{Isson2018a}. Formation of authigenic clays that scales with Ca and Mg concentration of riverine waters could decrease the \COtwo consumption associated with silicate weathering although the overall trend seen in this study would remain.

@@

We use temperature and runoff fields from a subset of the GFDL CM2.0 experiments (\citealp{Delworth2006a, Delworth2006b}; available for download at \url{https://nomads.gfdl.noaa.gov/dods-data/gfdl_cm2_0/}) for the climate model component of GEOCLIM. These experiments were performed in order to explore the effect of various changes in forcing agents on climate since ca. 1860 at 2.0\degrees $\times$ 2.5\degrees resolution. In the ``1860 control'' experiment, forcing agents representative of conditions ca. 1860 (including \COtwo, CH$_{4}$, N$_{2}$O, O$_{3}$, sulfates, carbon, dust, sea salt, solar irradiance, and the distribution of land cover types) are held constant for 500 years after reaching equilibrium. \pCOtwo in 1860 is assumed to be 286~ppm. In the ``+1\%/yr to 2$\times$'' experiment, initial conditions are taken from the ``1860 control'' experiment, then \pCOtwo is prescribed to increase from 286~ppm at a compounded rate of +1\% per year for 70 years, when \pCOtwo reaches double (572~ppm) of the initial value. \pCOtwo is then held constant until the end of the 280 year experiment. All non-\COtwo forcing agents are held constant. The ``+1\%/yr to 4$\times$'' experiment is identical to the ``+1\%/yr to 2$\times$'' experiment, except that \pCOtwo is prescribed to increase for 140 years, when \pCOtwo reaches quadruple (1144~ppm) of the initial value. \pCOtwo is then held constant for 160 years. We take the mean of the last 100 years of each of these three experiments (when \pCOtwo is being held constant at its final level) to obtain temperature and runoff fields for 286, 572, and 1144~ppm respectively. Temperature and runoff fields associated with \pCOtwo values between the three modeled \pCOtwo levels (286, 572, and 1144~ppm) are obtained through linear interpolation between the model results. Given that precipitation in this region is primarily driven by large-scale convective upwelling leading to high precipitation over both land and water, the current approach is a reasonable approximation for I\&NG. However, for paleogeographic change that would have very significantly modified precipitation over broad swathes of land such as growth of the Himalaya, this approach of using modern climate model results is not viable.

@@

We use geological data to quantify the changes in the area of I\&NG over the past 20~m.y. (described in detail in \textit{Paleoshoreline Reconstruction and Geological Synthesis}). To generate the lithologic map used in the ``removed I\&NG'' scenario (Fig. \ref{fig:ING_fracs}), we remove all land associated with arc-continent collision in I\&NG. To generate the lithologic map used in the ``reduced I\&NG + Sunda Shelf'' scenarios (Fig. \ref{fig:ING_fracs}), we take the estimated paleoshorelines of I\&NG for 15, 10, and 5~Ma, then remove all land that falls outside of these bounds. The slope and lithologic classification of each pixel is identical to that of the present day, provided that these pixels fall within the estimated paleoshorelines of I\&NG for their respective time slice. This means that while we are changing the amount of emergent land, we are not changing the latitudinal or longitudinal position and are keeping the slope of emerged pixels the same. Given that similar distributions of lithology and slope are reasonable in the past and that latitudinal translation has been relatively minor, we consider this simplification to be reasonable to first-order. We then add land that is not exposed today (i.e. the Sunda Shelf). However, the assignment of lithology, runoff, and slope for pixels on the Sunda Shelf is not trivial, given that the shelf is not currently exposed. As discussed in \textit{Paleoshoreline Reconstruction and Geological Synthesis}, the Sunda Shelf is a flat-lying, relatively stable platform of continental crust. Islands between Malaysia/Sumatra and Borneo are composed of granite and are surrounded by shallow marine siliciclastic sediments \citep{Darmadi2007a, Hall2009a, Hall2013b}. However, basement highs do not appear in the Gulf of Thailand, and seismic and drill core data suggest siliciclastic fluvial systems draining out toward the South China Sea when the shelf was exposed \citep{Darmadi2007a}. We therefore assign pixels of the Sunda Shelf between Malaysia/Sumatra and Borneo to be 50\% felsic and 50\% sediment, and pixels further to the north to be 100\% sediment. For the slope, we take the mean slope value (0.0038~m/m) of relatively flat land on eastern Sumatra, and assign this value to all pixels of the Sunda Shelf.  For the runoff, we linearly interpolate along latitude bands between present-day land pixels to obtain runoff values for the presently-submerged Sunda Shelf. This approach preserves large N-S variation in runoff associated with the large-scale Hadley circulation and therefore should be reasonable to first-order, although it does not accurately capture the smaller-scale interactions between land and ocean/atmosphere circulation.

To explore the sensitivity of our results to the inclusion of the Sunda Shelf, we also tested ``reduced I\&NG'' scenarios for 15, 10, and 5~Ma, which are identical to that of the ``reduced I\&NG + Sunda Shelf'' scenarios without the addition of the Sunda Shelf. We find that the estimated steady state \pCOtwo's for the ``reduced I\&NG'' scenarios are only marginally higher than those of the ``reduced I\&NG + Sunda Shelf'' scenarios (Fig. \ref{fig:scenario_pCO2_all}), suggesting that our results are relatively insensitive to the inclusion of the Sunda Shelf. This insensitivity can be attributed to the low Ca+Mg concentrations of felsic and sediment lithologies in conjunction with the low relief across the shelf.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{Manuscript/Figures/pCO2_proxies.pdf}
    \caption{Proxy-based \pCOtwo estimates for the past 20~m.y. For data that was compiled within \citet{Foster2017a}, error bars indicate standardized uncertainties. For the \citet{Ji2018a} data, error bars represent the 16-84$^{th}$ percentile of resampled estimates. The \citet{Bereiter2015a} data comes from the EPICA Dome C ice core.}
    \label{fig:pCO2_proxies}
\end{figure}

@@
